The Astropy Project

### 2017-10-26 main.tex
remove line break

    \item[Solar System Ephemerides]
    Also new is support for computing ephemerides of major solar system bodies
    and outputting the resulting positions as coordinate objects.
    These ephemerides can be computed either using analytic approximations from
    ERFA, or from downloaded JPL ephemerides (the latter requires the \package{j
    plephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
    optional dependency and an internet connection).
    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
    a specific body and choice of ephemeris source.

>>>>

    \item[Solar System Ephemerides]
    Also new is support for computing ephemerides of major solar system bodies
    and outputting the resulting positions as coordinate objects.
    These ephemerides can be computed either using analytic approximations from
    ERFA, or from downloaded JPL ephemerides (the latter requires the
    \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
    optional dependency and an internet connection).
    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
    a specific body and choice of ephemeris source.
